Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-14 doc/JFLA2022/paper.tex
reserve 'bridge' for gaia-hydras
more book comparison stuff

Given the objectives of \community, we believe it makes sense to propose a transfer anytime we encounter an interesting Coq project that is insufficiently maintained.
%
After a transfer, the \community maintainers are explicitly allowed to perform large changes and refactorings.
%
This means, for instance, that we can consolidate libraries by merging them, or split them up into several packages.

@@

\begin{table}
  \centering
  \footnotesize
  \begin{tabular}{lll}
  \hline
  \textbf{Title} & \textbf{Year} & \textbf{Category}\\
  \hline
  Coq'Art~\cite{BC04} & 2004 & Traditional\\
  Software Foundations~\cite{Pierce2007} & 2007 & Executable\\
  Certified Programming with Dependent Types~\cite{chlipalacpdt2011} & 2011 &  Executable\\
  Program Logics for Certified Compilers~\cite{Appel2014} & 2014 & Traditional\\
  Programs and Proofs~\cite{Sergey:PnP} & 2014 & Executable\\
  Formal Reasoning About Programs~\cite{Chlipala2017} & 2017 & Traditional\\
  Computer Arithmetic and Formal Proofs~\cite{Boldo2017} & 2017 & Traditional\\
  Mathematical Components~\cite{MCB} & 2018 & Traditional\\
  \hline
  \end{tabular}
  \caption{Coq book comparison.}
  \label{tbl:books}
\end{table}

@@

@@

\Hydras wants to be a bridge between scientific literature (\emph{e.g.},~\cite{KP82, KS81, schutte}) and proof assistant technology. For the mathematician, it may give a concrete view of the mathematical content, not only through full proofs, but also through significative computations: examples, functions associated with constructive proofs, etc. For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. %It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50K LOC), dependent on various tools and libraries of the \coq ecosystem, which  may be also used to experiment new techniques of continuous maintenance of the code and its documentation.

>>>>

Given the objectives of \community, we believe it makes sense to propose a transfer anytime we encounter an interesting Coq project that is insufficiently maintained.
%
After a transfer, the \community maintainers are explicitly allowed to perform large changes and refactorings.
%
This means, for instance, that we can consolidate packages by merging them, or split up a single package into several packages.

@@

\begin{table}
  \centering
  \footnotesize
  \begin{tabular}{lll}
  \hline
  \textbf{Title} & \textbf{Year} & \textbf{Category}\\
  \hline
  Coq'Art~\cite{BC04} & 2004 & Traditional\\
  Software Foundations~\cite{SF} & 2007 & Executable\\
  Certified Programming with Dependent Types~\cite{chlipalacpdt2011} & 2011 &  Executable\\
  Program Logics for Certified Compilers~\cite{Appel2014} & 2014 & Traditional\\
  Programs and Proofs~\cite{Sergey:PnP} & 2014 & Executable\\
  Formal Reasoning About Programs~\cite{Chlipala2017} & 2017 & Traditional\\
  Computer Arithmetic and Formal Proofs~\cite{Boldo2017} & 2017 & Traditional\\
  Mathematical Components~\cite{MCB} & 2018 & Traditional\\
  \hline
  \end{tabular}
  \caption{Coq book comparison.}
  \label{tbl:books}
\end{table}

@@

Due to our reliance on LaTeX for writing the book, obtaining a book representation in HTML is more cumbersome than for executable books such as Software Foundations~\cite{SF} and Certified Programming with Dependent Types~\cite{chlipalacpdt2011}. Currently, we generate the Coq code documentation as HTML separately from the book.

@@

\Hydras wants to be provide a connection between scientific literature (\emph{e.g.},~\cite{KP82, KS81, schutte}) and proof assistant technology. For the mathematician, it may give a concrete view of the mathematical content, not only through full proofs, but also through significative computations: examples, functions associated with constructive proofs, etc. For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. %It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50K LOC), dependent on various tools and libraries of the \coq ecosystem, which  may be also used to experiment new techniques of continuous maintenance of the code and its documentation.
